

```{r}
library(tidyverse)
library(gapminder)
library(knitr)
library(ggplot2)
data(gapminder)
glimpse(gapminder)
```

#Question 1)

#(A)

```{r}
gapminder %>%
  filter(country == "United States") %>%
  select(year)
```
These are years of available date for the United States.

1952				
1957				
1962				
1967				
1972				
1977				
1982				
1987				
1992				
1997
2002				
2007	

#(B)

```{r}
am <- filter(gapminder, continent == "Americas") 

distinct(am, year)
```
These are the years available in the Americas.

1952 1957 1962 1967 1972 1977 1982 1987 1992 1997 2002 2007

#Question 2

#(A)

```{r}
gapminder %>%
  filter(country == "United States") %>%
  filter(lifeExp > 70) %>%
  select(year, lifeExp)
```
Life expectancy exceeded 70 these years in the United States.

1962	70.210			
1967	70.760			
1972	71.340			
1977	73.380			
1982	74.650			
1987	75.020			
1992	76.090			
1997	76.810			
2002	77.310			
2007	78.242	

#(B)

```{r}
gapminder %>%
  filter(country == "Honduras") %>%
  filter(lifeExp > 70) %>%
  select(year, country, lifeExp)
```
Life expectancy exceeded 70 this year in Honduras.

2007	Honduras	70.198	

#(C)

```{r}
gapminder %>%
  filter(lifeExp > 70) %>%
  filter(continent == "Americas") %>%
  group_by(country) %>%
  select(country, lifeExp) %>%
  summarize(mean_lifeExp = mean(lifeExp) )
```
Average life expectancy when 70 years was exceeded in the Americas by country.

Argentina	          73.11540			
Brazil	            71.69800			
Canada	            76.01230			
Chile	              74.90200			
Colombia	          71.62800			
Costa Rica	        75.54714			
Cuba	              74.65738			
Dominican Republic	71.54100			
Ecuador	            73.82633			
El Salvador       	71.30600	
Guatemala         	70.25900			
Honduras          	70.19800			
Jamaica           	71.67600			
Mexico            	74.05550			
Nicaragua         	71.86750			
Panama            	73.07400			
Paraguay          	71.25350			
Peru              	71.42100			
Puerto Rico        	74.49244			
United States     	74.38120	
Uruguay	            73.56483			
Venezuela         	71.99980

#Question 3

#(A)

```{r}
gapminder %>%
  filter(pop > 1000000000) %>%
  filter(year == "2007") %>%
  select(year, country, pop)
```
China and India had a population over a billion in 2007.

2007	China	1318683096		
2007	India	1110396331

#(B)

```{r}
gapminder %>%
  filter(pop > 1000000000) %>%
  select(year, country, pop) %>%
  arrange(year) %>%
  head(n=10)
```
China reached a population of a billion first in 1982.

1982	China	1000281000	

#Question 4

#(A)

```{r}
gapminder %>%
  filter(year == 2007) %>%
  select(year, country, gdpPercap) %>%
  arrange(gdpPercap) %>%
  head(n=10)
```
In 2007 these three countries had the lowest per capita GDP.

2007	Congo, Dem. Rep.	277.5519		
2007	Liberia	          414.5073		
2007	Burundi	          430.0707		

#(B)

```{r}
gapminder %>%
  filter(year == 1962) %>%
  select(year, country, gdpPercap) %>%
  arrange(gdpPercap) %>%
  head(n=10)
```
In 1962 these three countries had the lowest per capita GDP.

1962	Burundi	355.2032		
1962	Eritrea	380.9958		
1962	Myanmar	388.0000	

#(C)

The majority of the countries are in Africa with bottom 3 per capita GDP.

#Question 5

#(A)

```{r}
plot(gapminder$gdpPercap, gapminder$lifeExp)
```

#(B)

```{r}
plot(log(gapminder$gdpPercap), log(gapminder$lifeExp))
```

#(C)

```{r}
 qplot(log(gdpPercap), log(lifeExp), colour = continent, data = gapminder)
```

#(D)

Lower GDP and High Life Expectany:
A lot of Asia
Some of the America
Some of the Africa
Some of the Europe


High GDP and High Life Expectany:
A lot of Europe
A lot of Oceania
Some of the America
Some of the Asia


